---
title: "Intro to basics"
output:
  html_notebook:
    df_print: paged
  html_document:
    df_print: paged
---

## R Objetcs

### Variable Assignment
Save information as an R objetc with the *greater than* sign followed by *a minus*, e.g. an arrow: `<-`
```{r}
#name of new objetc         assignment operator, "gets"         information to store in the objetc
    foo                                 <-                            42
```

### Common R Workflow
Save output of one function as an R objetc to use in a second function
```{r}
foo <- round(3.1415) + 1
foo
```

```{r}
factorial(foo)
```

## Remove objetcs from environment
You can remove an objetc with `rm`
```{r}
fac_foo<-factorial(foo)
fac_foo
```

```{r}
rm(foo)
rm(fac_foo)
```

### To consider...

- Object names cannot beggin with numbers. Wise to avoid names already in use.

- R will treat the lowercase and capital letters as different.


## Data Structures

You ca save more than a single number in an objetc by creating a *vector*, *matrix*, or *array*.

```{r}
WorldPhones
```


### Vectors

- Combine multiple elements into one dimensional array.

- Create with the `c` function.
```{r}
vec<-c(1,2,3,10,100)
vec
```

### Matrices

- Multiple elements stored in a two dimensional array.

- Create with the `matrix` function.
